---
title: "ABCD Script Lahey Analyses"
author: "Carlos Cardenas-Iniguez"
date: "4/22/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packagesneeded}
library(dplyr) 
library(ggplot2) 
library(lme4)
library(cvTools)
library(summarytools)
library(readr)
library(fastDummies)
```
```{r directories}
# set directory
data_dir <- "/Volumes/ToshibaExt/ABCD/ABCDstudyDEAP(1)_2.0" #This should be a path to the folder with all the ABCD Release 2.0 text files
data_dir_1 <- "/Volumes/ToshibaExt/ABCD/ABCDFixRelease_2.0.1" #This should be a path to the folder with all of the ABCD Release 2.0.1 text files (for the accurate DTI and structural files)
project_folder <- "/Volumes/ToshibaExt/ABCD/Lahey/"
setwd(project_folder) #write in output folder if different than project folder, this needs to be run in the console, or it won't properly do it

```

The following section pulls all of the phenotype and demographic files. please see the codebook for additional details on the instruments below. 
```{r phenotype_variables}
acspsw03_n <-   sprintf('%s/acspsw03.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
acspsw03 <- sprintf('%s/acspsw03.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = acspsw03_n) %>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(src_subject_id, subjectkey, eventname, interview_date,
         interview_age, gender, race_ethnicity, rel_family_id,
         rel_group_id, rel_ingroup_order, rel_relationship, 
         rel_same_sex, acs_raked_propensity_score)

abcd_lt01_n <-   sprintf('%s/abcd_lt01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
abcd_lt01 <- sprintf('%s/abcd_lt01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = abcd_lt01_n) %>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(src_subject_id,site_id_l)

abcd_mri01_n <-   sprintf('%s/abcd_mri01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
abcd_mri01 <- sprintf('%s/abcd_mri01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = abcd_mri01_n) %>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(src_subject_id,
         mri_info_manufacturer,
         mri_info_manufacturersmn,
         mri_info_deviceserialnumber)

pdem02_n <-   sprintf('%s/pdem02.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
pdem02 <- sprintf('%s/pdem02.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = pdem02_n, 
           na = c('','NA'), guess_max = 11875) %>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(src_subject_id, demo_prim_p)

dhx01_n <-   sprintf('%s/dhx01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
dhx01  <- sprintf('%s/dhx01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = dhx01_n, 
           na = c('','NA'), guess_max = 11875) %>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(src_subject_id,
         devhx_1_p,
         devhx_2_birth_wt_lbs_p,
         devhx_2b_birth_wt_oz_p,
         devhx_3_age_at_birth_mother_p,
         devhx_4_age_at_birth_father_p,
         devhx_5_twin_p,
         devhx_8_tobacco_p,
         devhx_8_cigs_per_day_p,
         devhx_8_alcohol_p,
         devhx_8_alchohol_max_p,
         devhx_8_alchohol_avg_p,
         devhx_8_marijuana_p,
         devhx_8_marijuana_amt_p,
         devhx_8_coc_crack_p,
         devhx_8_coc_crack_amt_p,
         devhx_8_her_morph_p,
         devhx_8_her_morph_amt_p,
         devhx_8_oxycont_p,
         devhx_8_oxycont_amt_p,
         devhx_8_other_drugs_p,
         devhx_9_tobacco_p,
         devhx_9_cigs_per_day_p,
         devhx_9_alcohol_p,
         devhx_9_alcohol_max_p,
         devhx_9_alcohol_max_dk_p,
         devhx_9_alcohol_avg_p,
         devhx_9_marijuana_p,
         devhx_9_marijuana_amt_p,
         devhx_9_coc_crack_p,
         devhx_9_coc_crack_amt_p,
         devhx_9_her_morph_p,
         devhx_9_oxycont_p,
         devhx_9_oxycont_amt_p,
         devhx_9_other_drugs_p,
         devhx_10_p,
         devhx_caffeine_11_p,
         devhx_caffeine_amt_p,
         devhx_caff_amt_week_p,
         devhx_12a_born_premature_p,
         devhx_12_weeks_premature_p
  )

pasr01_n <-   sprintf('%s/pasr01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
pasr01  <- sprintf('%s/pasr01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = pasr01_n, 
           na = c('','NA'), guess_max = 11875) %>% 
  filter(eventname=="baseline_year_1_arm_1") %>% 
  select(c(5,11:146))

abcd_bpm01_n <-   sprintf('%s/abcd_bpm01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
abcd_bpm01  <- sprintf('%s/abcd_bpm01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = abcd_bpm01_n, na = c('','NA')) %>% 
  filter(eventname=="baseline_year_1_arm_1") 

abcd_bpmt01_n <-   sprintf('%s/abcd_bpmt01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
abcd_bpmt01  <- sprintf('%s/abcd_bpmt01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = abcd_bpmt01_n, na = c('','NA')) %>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5,10:27))

abcd_cbcl01_n <-   sprintf('%s/abcd_cbcl01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
abcd_cbcl01 <- sprintf('%s/abcd_cbcl01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = abcd_cbcl01_n, 
           na = c('','NA'), guess_max = 11875) %>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5,10:128))
#####also available at 1 yr followup for a subset of participants
##### only baseline included here

abcd_ptsd01_n <-   sprintf('%s/abcd_ptsd01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
abcd_ptsd01 <- sprintf('%s/abcd_ptsd01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = abcd_ptsd01_n, 
           na = c('','NA'), guess_max = 11875) %>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5,10:26))
####only available for 11860 participants

abcd_ksad01_n <-   sprintf('%s/abcd_ksad01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
abcd_ksad01<- sprintf('%s/abcd_ksad01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = abcd_ksad01_n, 
           na = c('','NA'), guess_max = 11875) %>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select( c(5, 11:18,19:57,58:67,68:110,111:115,116:142,143:158,159:187,
            188:202,203:215,216:264,265:290,309:346,347:399,400:424,425:458,
            835:893,465:471,894:948)) 

##### only available for 11860 participants at baseline
#####also available at 1 yr followup for a subset of participants
##### only baseline included here

abcd_ksad501_n <-   sprintf('%s/abcd_ksad501.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
abcd_ksad501<- sprintf('%s/abcd_ksad501.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = abcd_ksad501_n, 
           na = c('','NA'), guess_max = 11875) %>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(sort(names(.)))  %>% 
  select(c(963,9:55,56:73,74:99,118:155,156:208,209:233,234:267,
           274:280,317:369,697:751,752:755,756:804,805:810,823:827,
           828:870,871:886,887:899,900:927,928:946,947:959)) %>%
  select(-c(ksads_8_313b_t))
colnames(abcd_ksad501)[colnames(abcd_ksad501)=="ksads_8_313a_t"] <- "ksads_8_313_t"

#####Only available for 11866 participants at baseline
#####also available at 1 yr followup for a subset of participants
##### only baseline included here

abcd_y7mi01_n <-   sprintf('%s/abcd_y7mi01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
abcd_y7mi01 <- sprintf('%s/abcd_y7mi01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = abcd_y7mi01_n, na = c('','NA')) %>% 
  filter(eventname=="baseline_year_1_arm_1")
######only at 1 year followup

abcd_yddss01_n <-   sprintf('%s/abcd_yddss01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
abcd_yddss01 <- sprintf('%s/abcd_yddss01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = abcd_yddss01_n, na = c('','NA')) %>% 
  filter(eventname=="baseline_year_1_arm_1")
######only at 1 year followup

cct01_n <-   sprintf('%s/cct01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
cct01  <- sprintf('%s/cct01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = cct01_n, na = c('','NA')) %>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(src_subject_id, neurocog_cash_choice_task)

psb01_n <-   sprintf('%s/psb01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
psb01<- sprintf('%s/psb01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = psb01_n, 
           na = c('','NA'), guess_max = 11875) %>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5,11:13))
#####also available at 1 yr followup for a subset of participants
##### only baseline included here

abcd_psb01_n <-   sprintf('%s/abcd_psb01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
abcd_psb01<- sprintf('%s/abcd_psb01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = abcd_psb01_n, 
           na = c('','NA'), guess_max = 11875) %>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(5,10:12)
#####also available at 1 yr followup for a subset of participants
##### only baseline included here

abcd_upps01_n <-   sprintf('%s/abcd_upps01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
abcd_upps01<- sprintf('%s/abcd_upps01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = abcd_upps01_n, 
           na = c('','NA'), guess_max = 11875) %>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5,10:29))

abcd_lsstbi01_n <-   sprintf('%s/abcd_lsstbi01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
abcd_lsstbi01  <- sprintf('%s/abcd_lsstbi01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = abcd_lsstbi01_n, 
           na = c('','NA'), guess_max = 11875) %>% 
  filter(eventname=="1_year_follow_up_y_arm_1")
#####abcd_lsstbi01 only available at one-year followup 
#####for a portion of participants (4951) as of release 2.0

dibf01_n <-   sprintf('%s/dibf01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
dibf01<- sprintf('%s/dibf01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = dibf01_n, 
           na = c('','NA'), guess_max = 11875) %>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5,39:46,49:56,60:64,70,71,73:81))

abcd_tbss01_n <-   sprintf('%s/abcd_tbss01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
abcd_tbss01 <- sprintf('%s/abcd_tbss01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = abcd_tbss01_n, 
           na = c('','NA'), guess_max = 11875) %>% 
  filter(eventname=="baseline_year_1_arm_1") %>% 
  select(src_subject_id,
         nihtbx_picvocab_uncorrected,
         nihtbx_flanker_uncorrected,
         nihtbx_list_uncorrected,
         nihtbx_cardsort_uncorrected,
         nihtbx_pattern_uncorrected,
         nihtbx_picture_uncorrected,
         nihtbx_reading_uncorrected)

abcd_ps01_n <-   sprintf('%s/abcd_ps01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
abcd_ps01  <- sprintf('%s/abcd_ps01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = abcd_ps01_n, 
           na = c('','NA'), guess_max = 11875) %>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(src_subject_id, 
         pea_ravlt_sd_trial_i_tc,
         pea_ravlt_sd_trial_ii_tc,
         pea_ravlt_sd_trial_iii_tc,
         pea_ravlt_sd_trial_iv_tc,
         pea_ravlt_sd_trial_v_tc,
         pea_ravlt_sd_listb_tc,
         pea_ravlt_sd_trial_vi_tc,
         pea_ravlt_ld_trial_vii_tc,
         pea_wiscv_trs)

lmtp201_n <-   sprintf('%s/lmtp201.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
lmtp201  <- sprintf('%s/lmtp201.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = lmtp201_n, 
           na = c('','NA'), guess_max = 11875) %>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(src_subject_id,
         lmt_scr_perc_correct)

medsy01_n <-   sprintf('%s/medsy01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
medsy01  <- sprintf('%s/medsy01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = medsy01_n, 
           na = c('','NA'), guess_max = 11875) %>% 
  filter(eventname=="1_year_follow_up_y_arm_1") 


abcd_mx01_n <-   sprintf('%s/abcd_mx01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
abcd_mx01 <- sprintf('%s/abcd_mx01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = abcd_mx01_n, 
           na = c('','NA'), guess_max = 11875) %>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(src_subject_id,
         medhx_1a_dr_past_yr_p,
         medhx_2c_brain_injury_p,
         medhx_4a_er_past_yr_p,
         medhx_6a_broken_bones_p,
         medhx_6b_sprains_p,
         medhx_6c_cuts_p,
         medhx_6d_stitches_p,
         medhx_6e_other_wounds_p,
         medhx_6f_falls_p,
         medhx_6g_burns_p,
         medhx_6i_head_injury_p,
         medhx_6j_unconsious_p,
         medhx_6m_broken_teeth_p,
         medhx_6q_poison_p,
         medhx_6r_gun_shot_p,
         medhx_6s_knife_wound_p)

acspsw03_ben <- acspsw03
acspsw03_ben$race_ethnicity <- factor(acspsw03$race_ethnicity, levels = 1:5,
                                  labels = c("white", "black","hispanic","asian", "other"))
acspsw03_ben <- acspsw03_ben %>% dummy_cols(ignore_na = TRUE, select_columns = c("race_ethnicity", "gender"))%>%
  select(src_subject_id, 
         interview_age,
         gender_M,
         gender_F,
         race_ethnicity_white,
         race_ethnicity_black,
         race_ethnicity_hispanic,
         race_ethnicity_asian,
         race_ethnicity_other,
         race_ethnicity,
         gender,
         acs_raked_propensity_score)

acspsw03_ben_fam <- acspsw03
acspsw03_ben_fam <- acspsw03_ben_fam %>%
  select(src_subject_id,
         rel_family_id)

abcd_ps01_ben <- abcd_ps01
abcd_ps01_ben$pea_ravlt_sd_trialmean <- rowMeans(abcd_ps01_ben[,c(2:6)])

pdem02_fam_n <-   sprintf('%s/pdem02.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
pdem02_fam <- sprintf('%s/pdem02.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = pdem02_fam_n, 
           na = c('','NA'), guess_max = 11875) %>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(src_subject_id,
         demo_prnt_ed_v2b,
         demo_prnt_gender_id_p,
         demo_prtnr_ed_v2b,
         demo_prnt_prtnr_bio_2,
         demo_prnt_prtnr_adopt_p,
         demo_comb_income_v2b,
         demo_roster_p)
```
####################################################################################
######################################################################################
####################################################################################
The following are extra variables that were used for sensitivity analyses for the Phenotypes paper. Should still be run

```{r additionalvars}
abcd_pksadscd01_n <-   sprintf('%s/abcd_pksadscd01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
abcd_pksadscd01 <- sprintf('%s/abcd_pksadscd01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = abcd_pksadscd01_n, 
           na = c('','NA'), guess_max = 16800) %>% 
  filter(eventname=="baseline_year_1_arm_1")

abcd_y7mi01_n <-   sprintf('%s/abcd_y7mi01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
abcd_y7mi01 <- sprintf('%s/abcd_y7mi01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = abcd_y7mi01_n, 
           na = c('','NA'), guess_max = 16800)

pps01_n <-   sprintf('%s/pps01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
pps_01 <- sprintf('%s/pps01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = pps01_n, 
           na = c('','NA'), guess_max = 16800)%>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5,10:72))

abcd_ehis01_n <-   sprintf('%s/abcd_ehis01.txt',data_dir) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
abcd_ehis01  <- sprintf('%s/abcd_ehis01.txt',data_dir) %>% 
  read_tsv(skip = 2, col_names = abcd_ehis01_n, 
           na = c('','NA'), guess_max = 16800)%>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(src_subject_id,
         ehi_ss_score)
```
#######################################################################################
# BPPCA Scores from Thompson et al. 2019 
# Run for Ben's stuff
# Needs csv file with BPPCA scores extracted

```{r BPPCA_CogScores}
BPPCA_CogScores <-   "/Volumes/ToshibaExt/ABCD_release2.0.1_update_Rds/BPPCA_CogScores.csv" %>%
  read_csv(guess_max = 16800) %>%
  select(src_subject_id, 
         neurocog_pc1,
         neurocog_pc2,
         neurocog_pc3)
```
```{r fsqc_cores}
 freesqc01_n <- sprintf('%s/freesqc01.txt',data_dir_1) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
 freesqc01 <- sprintf('%s/freesqc01.txt',data_dir_1) %>% 
  read_tsv(skip = 2, col_names = freesqc01_n, 
           na = c('','NA'), guess_max = 16800)%>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(src_subject_id,
         fsqc_qc)
```

#######################################################################################
#Estimated factor scores from SEM analyses
#Bifactor Model Scores
Do not need to include these for Ben
For this to run, you will need to have the Bifactor scores csv

```{r BifactorScores}
CBCL_BifactorScores <-   sprintf('%s/CBCL_BifactorEstimatedFactorScores.csv',project_folder) %>%
  read_csv(guess_max = 16800) %>%
  select(src_subject_id, 
         Gen3B,
         Ext3B,
         Int3B,
         ADHD3B)
```

This section will collect all of the DTI measures (FA, MD, TD, LD )
```{r WhiteMatter}
# DTI Measures #
wm_fa_n <- sprintf('%s/abcd_dmdtifp101.txt',data_dir_1) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
wm_fa <- sprintf('%s/abcd_dmdtifp101.txt',data_dir_1) %>% 
  read_tsv(skip = 2, col_names = wm_fa_n, 
           na = c('','NA'), guess_max = 16800)%>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5,10:51))

wm_md_n <- sprintf('%s/abcd_dmdtifp101.txt',data_dir_1) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
wm_md <- sprintf('%s/abcd_dmdtifp101.txt',data_dir_1) %>% 
  read_tsv(skip = 2, col_names = wm_md_n, 
           na = c('','NA'), guess_max = 16800)%>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5,52:93))

wm_ld_n <- sprintf('%s/abcd_dmdtifp101.txt',data_dir_1) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
wm_ld <- sprintf('%s/abcd_dmdtifp101.txt',data_dir_1) %>% 
  read_tsv(skip = 2, col_names = wm_ld_n, 
           na = c('','NA'), guess_max = 16800)%>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5,94:135))

wm_td_n <- sprintf('%s/abcd_dmdtifp101.txt',data_dir_1) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
wm_td <- sprintf('%s/abcd_dmdtifp101.txt',data_dir_1) %>% 
  read_tsv(skip = 2, col_names = wm_td_n, 
           na = c('','NA'), guess_max = 16800)%>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5, 136:177))
```


#########################################################################################
#########################################################################################
### Cortical Structure Measures--Desikan-Killiany Parcellation
```{r StructuralDesikanKilliany}
#Cortical Thickness
ct_dk_n <- sprintf('%s/abcd_smrip101.txt',data_dir_1) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
ct_dk <- sprintf('%s/abcd_smrip101.txt',data_dir_1) %>% 
  read_tsv(skip = 2, col_names = ct_dk_n, 
           na = c('','NA'), guess_max = 16800)%>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5, 11:78,115:117))

#Sulcal Depth
sd_dk_n <- sprintf('%s/abcd_smrip101.txt',data_dir_1) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
sd_dk <- sprintf('%s/abcd_smrip101.txt',data_dir_1) %>% 
  read_tsv(skip = 2, col_names = sd_dk_n, 
           na = c('','NA'), guess_max = 16800)%>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5, 118:185,222:224))

#Cortical Area
ca_dk_n <- sprintf('%s/abcd_smrip101.txt',data_dir_1) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
ca_dk <- sprintf('%s/abcd_smrip101.txt',data_dir_1) %>% 
  read_tsv(skip = 2, col_names = ca_dk_n, 
           na = c('','NA'), guess_max = 16800)%>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5, 225:292,329:331))

#Cortical Volume
cv_dk_n <- sprintf('%s/abcd_smrip101.txt',data_dir_1) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
cv_dk <- sprintf('%s/abcd_smrip101.txt',data_dir_1) %>% 
  read_tsv(skip = 2, col_names = cv_dk_n, 
           na = c('','NA'), guess_max = 16800)%>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5, 332:399,436:438))

#T1 Intensity white matter 
t1wm_dk_n <- sprintf('%s/abcd_smrip101.txt',data_dir_1) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
t1wm_dk <- sprintf('%s/abcd_smrip101.txt',data_dir_1) %>% 
  read_tsv(skip = 2, col_names = t1wm_dk_n, 
           na = c('','NA'), guess_max = 16800)%>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5, 439:506,543:545))

#T1 Intensity Gray matter 
t1gm_dk_n <- sprintf('%s/abcd_smrip101.txt',data_dir_1) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
t1gm_dk <- sprintf('%s/abcd_smrip101.txt',data_dir_1) %>% 
  read_tsv(skip = 2, col_names = t1gm_dk_n, 
           na = c('','NA'), guess_max = 16800)%>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5, 546:613,650:652))

#T1 gray-white intensity contrast
t1cont_dk_n <- sprintf('%s/abcd_smrip101.txt',data_dir_1) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
t1cont_dk <- sprintf('%s/abcd_smrip101.txt',data_dir_1) %>% 
  read_tsv(skip = 2, col_names = t1cont_dk_n, 
           na = c('','NA'), guess_max = 16800)%>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5, 653:720,757:759))

#Subcort Volume 
subcort_dk_n <- sprintf('%s/abcd_smrip201.txt',data_dir_1) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
subcort_dk <- sprintf('%s/abcd_smrip201.txt',data_dir_1) %>% 
  read_tsv(skip = 2, col_names = subcort_dk_n, 
           na = c('','NA'), guess_max = 16800)%>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5, 330:375))

subcort_icv <- subcort_dk[,c(1,45)]
```

#########################################################################################
#########################################################################################
### Cortical Structure Measures--Destrieux Parcellation
```{r StructuralDestrieux}
#Cortical Thickness
ct_ds_n <- sprintf('%s/abcd_mrisdp101.txt',data_dir_1) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
ct_ds <- sprintf('%s/abcd_mrisdp101.txt',data_dir_1) %>% 
  read_tsv(skip = 2, col_names = ct_ds_n, 
           na = c('','NA'), guess_max = 16800)%>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5, 10:160))

#Sulcal Depth
sd_ds_n <- sprintf('%s/abcd_mrisdp101.txt',data_dir_1) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
sd_ds <- sprintf('%s/abcd_mrisdp101.txt',data_dir_1) %>% 
  read_tsv(skip = 2, col_names = sd_ds_n, 
           na = c('','NA'), guess_max = 16800)%>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5, 161:311))

#Cortical Area
ca_ds_n <- sprintf('%s/abcd_mrisdp101.txt',data_dir_1) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
ca_ds <- sprintf('%s/abcd_mrisdp101.txt',data_dir_1) %>% 
  read_tsv(skip = 2, col_names = ca_ds_n, 
           na = c('','NA'), guess_max = 16800)%>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5, 312:462))

#Cortical Volume
cv_ds_n <- sprintf('%s/abcd_mrisdp101.txt',data_dir_1) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
cv_ds <- sprintf('%s/abcd_mrisdp101.txt',data_dir_1) %>% 
  read_tsv(skip = 2, col_names = cv_ds_n, 
           na = c('','NA'), guess_max = 16800)%>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5, 463:613))

#T1 Intensity white matter 
t1wm_ds_n <- sprintf('%s/abcd_mrisdp101.txt',data_dir_1) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
t1wm_ds <- sprintf('%s/abcd_mrisdp101.txt',data_dir_1) %>% 
  read_tsv(skip = 2, col_names = t1wm_ds_n, 
           na = c('','NA'), guess_max = 16800)%>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5, 614:764))

#T1 Intensity Gray matter 
t1gm_ds_n <- sprintf('%s/abcd_mrisdp101.txt',data_dir_1) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
t1gm_ds <- sprintf('%s/abcd_mrisdp101.txt',data_dir_1) %>% 
  read_tsv(skip = 2, col_names = t1gm_ds_n, 
           na = c('','NA'), guess_max = 16800)%>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5, 765:915))

#T1 gray-white intensity contrast
t1cont_ds_n <- sprintf('%s/abcd_mrisdp201.txt',data_dir_1) %>%
  read_tsv(n_max = 0) %>% # default: col_names = TRUE
  names()
t1cont_ds <- sprintf('%s/abcd_mrisdp201.txt',data_dir_1) %>% 
  read_tsv(skip = 2, col_names = t1cont_ds_n, 
           na = c('','NA'), guess_max = 16800)%>% 
  filter(eventname=="baseline_year_1_arm_1") %>%
  select(c(5, 10:160))
```
Run this for a dataset for the WM and phenotypes papers. It will output a .sav file for SPSS
and a .csv file. 
```{r SaveWMdataset}

###############################
#Here we combine all measures, and merge them all together. 

#all_measures  = list(acspsw03, abcd_lt01, abcd_mri01, pdem02, dhx01, pasr01, abcd_bpmt01, abcd_cbcl01,
#                     abcd_ptsd01, abcd_ksad01, abcd_ksad501, cct01, psb01, abcd_psb01,
#                     abcd_upps01, abcd_mx01, dibf01, abcd_tbss01, abcd_ps01, lmtp201, pps_01,abcd_ehis01,
#                     wm_fa, wm_ld, wm_md, wm_td, subcort_icv, BPPCA_CogScores, CBCL_BifactorScores)

all_measures  = list(acspsw03, abcd_lt01, abcd_mri01, pdem02, psb01, abcd_psb01,
                     abcd_tbss01,
                     wm_md, subcort_icv, BPPCA_CogScores, CBCL_BifactorScores, acspsw03_ben, freesqc01)

combined_measures <- Reduce(function(dtf1, dtf2) merge(dtf1, dtf2, all.x = TRUE),
       all_measures)

combined_measures_sorted <- combined_measures[order(combined_measures$src_subject_id),]
combined_measures_sorted <- combined_measures_sorted %>% 
  mutate(subnum_new = 1:n() + 10000) %>%
  mutate(subnum_char = sapply(subnum_new, toString)) %>%
  mutate(FLIP = subnum_new %% 10) %>%
  select(FLIP, subnum_char, subnum_new, everything())

#can save to desired format
write.csv(combined_measures_sorted, "ABCD_behcombined_wm_test2.csv", row.names = FALSE) 
#this will save csv with all behav measures and also all white matter variables

#The code below will save an SPSS-compatible .sav file
library(haven)
sav1<- write_sav(combined_measures_sorted, "ABCD_behcombined_wm_test2.sav", compress = FALSE)
```

You only need to run this section if you are extracting the cortical structure measures using the Desikan-Killiany parcellation

```{r SaveStructDKDataset}
struct_meas_dk <- list(acspsw03, ct_dk, sd_dk, ca_dk, cv_dk, t1gm_dk, t1wm_dk, t1cont_dk, subcort_dk)
combined_measures_struct_dk <- Reduce(function(dtf1, dtf2) left_join(dtf1, dtf2, by = "src_subject_id"),struct_meas_dk)

write.csv(combined_measures_struct_dk, "ABCD_struct_dk.csv", row.names = FALSE) 
#this will save csv with all structural measures using the Desikan-Killiany parcellation (and subcortical volumes)
```
You only need to run this section if you are extracting the cortical structure measures using the Destrieux parcellation
```{r SaveStructDSDataset}
struct_meas_ds <- list(acspsw03, ct_ds, sd_ds, ca_ds, cv_ds, t1gm_ds, t1wm_ds, t1cont_ds)
combined_measures_struct_ds <- Reduce(function(dtf1, dtf2) left_join(dtf1, dtf2, by = "src_subject_id"), struct_meas_ds)

write.csv(combined_measures_struct_ds, "ABCD_struct_ds.csv", row.names = FALSE) 
#this will save csv with all structural measures using the Destrieux parcellation 
```
You only need to run this section if you are extracting the white matter and additional bifactor model scores and demographics
```{r SaveWMforCanCorr}
measures_ben_wm <- list(acspsw03_ben, abcd_lt01, lmtp201, abcd_ps01_ben, abcd_tbss01, CBCL_BifactorScores,wm_fa, wm_ld, wm_md, wm_td,abcd_mri01,acspsw03_ben_fam, pdem02_fam)

combined_measures_ben_wm <-Reduce(function(dtf1, dtf2) left_join(dtf1, dtf2, by = "src_subject_id"),
                                  measures_ben_wm )

write.csv(combined_measures_ben_wm, "ABCD_wm_bifac_ef_measures.csv", row.names = FALSE)
#this will save csv with all the wm measures, all EF scores, all bifactor scores, and control demographics
```

```{r pca}
library(FactoMineR)
library(data.table)
ef_factors <- data.table(combined_measures$nihtbx_flanker_uncorrected, combined_measures$nihtbx_cardsort_uncorrected, combined_measures$nihtbx_pattern_uncorrected)
res.pca = PCA(ef_factors, scale.unit=TRUE, ncp=5)
pca1 <- res.pca$ind$coord[,1]
```


```{r vars_regressions}
mri_coil_dummy <- dummy_cols(combined_measures$mri_info_manufacturersmn)
colnames(mri_coil_dummy) <- c("mri_coil_dummy_orig", "coil_Achieva_dStream","coil_Discovery_MR750",
"coil_Ingenia","coil_Prisma","coil_Prisma_fit","coil_NA")

race_eth_dummy <- dummy_cols(combined_measures$race_ethnicity)
colnames(race_eth_dummy) <- c("race_eth_orig", "race_eth_white","race_eth_black",
"race_eth_hispanic","race_eth_asian","race_eth_other","other_NA")

gender_dummy <- dummy_cols(combined_measures$gender)
colnames(gender_dummy) <- c("gender_orig","gender_Female","gender_Male","gender_NA")

vars_for_regressions <- data.frame(combined_measures_sorted, mri_coil_dummy,race_eth_dummy, gender_dummy)
vars_for_reg <- vars_for_regressions[which(vars_for_regressions$fsqc_qc ==1),c(5,35:84,92,94:106,108:110)]
vars_for_reg_pass <- vars_for_regressions[which(vars_for_regressions$fsqc_qc ==1),]
vars_for_reg_pass_sample <- vars_for_regressions[,c(5,35:84,92,94:106,108:110)]

vars_for_reg_comp <- vars_for_reg_pass_sample[complete.cases(vars_for_reg_pass_sample),]
vars_reg_zscore <- data.frame(lapply(vars_for_reg_comp, function(x) scale(x)))

vars_for_corrplot <- vars_for_regressions[which(vars_for_regressions$fsqc_qc ==1),c(5,35:69,79,81:84)]
vars_for_corrplot_complete <- vars_for_corrplot[complete.cases(vars_for_corrplot),]
subsetef <- vars_for_corrplot_complete[,c(37:41)]
```
```{r corrplot}
library(corrplot)
vars_matrix <- data.matrix(vars_for_corrplot_complete)
M <- cor(vars_matrix)
corrplot(M, method = "color")

vars_matrix <- data.matrix(subsetef)
M1 <- cor(vars_matrix)
corrplot.mixed(M1, upper = "color", lower.col = "black")

```


```{r LV1Mediation_GenAbility}
fitM <- lm(neurocog_pc2~ dmdtifp1_43 + interview_age + gender_Male + race_eth_white + race_eth_black +race_eth_hispanic 
           +coil_Achieva_dStream + coil_Discovery_MR750 + coil_Ingenia + coil_Prisma,     data=vars_reg_zscore) 
fitY <- lm(ADHD3B~ neurocog_pc2 + dmdtifp1_43 + interview_age + gender_Male + race_eth_white + race_eth_black +race_eth_hispanic  
           +coil_Achieva_dStream + coil_Discovery_MR750 + coil_Ingenia + coil_Prisma, data=vars_reg_zscore)
fitMedBoot <- mediation:::mediate(fitM, fitY, boot=TRUE, sims=2000, treat="dmdtifp1_43", mediator="neurocog_pc2")
summary(fitMedBoot)
plot(fitMedBoot, main= "Mediation Effects for EF on ADHD")
```

```{r MediationDiagram_LV1_GenAbility}
library(psych)
fita_1 <- lm(neurocog_pc2~ dmdtifp1_43 + interview_age + gender_Male + race_eth_white + race_eth_black +race_eth_hispanic 
           +coil_Achieva_dStream + coil_Discovery_MR750 + coil_Ingenia + coil_Prisma, data=vars_for_reg_comp) 
fitcp_1 <- lm(ADHD3B~ neurocog_pc2 + dmdtifp1_43 + interview_age + gender_Male + race_eth_white + race_eth_black +race_eth_hispanic  
           +coil_Achieva_dStream + coil_Discovery_MR750 + coil_Ingenia + coil_Prisma, data=vars_reg_zscore)
fitb_1 <- lm(ADHD3B~ neurocog_pc2 + interview_age + gender_Male + race_eth_white + race_eth_black +race_eth_hispanic  
           +coil_Achieva_dStream + coil_Discovery_MR750 + coil_Ingenia + coil_Prisma, data=vars_reg_zscore)
fitc_1 <-lm(ADHD3B~dmdtifp1_43 + interview_age +gender_Male + race_eth_white + race_eth_black +race_eth_hispanic  
           +coil_Achieva_dStream + coil_Discovery_MR750 + coil_Ingenia + coil_Prisma, data=vars_reg_zscore)
mod1Cog <- psych:::mediate(ADHD3B ~ dmdtifp1_43 - interview_age - gender_Male -race_eth_white - race_eth_black - race_eth_hispanic 
           - coil_Achieva_dStream - coil_Discovery_MR750 - coil_Ingenia - coil_Prisma + (neurocog_pc2), data=vars_reg_zscore, n.iter = 10000, std = TRUE) #, std = TRUE
psych:::mediate.diagram(mod1Cog, xlim = c(-1,11), ylim= c(3,9))
```

```{r mediatetable_LV1_GenAbility, results='asis'}
library(stargazer)
stargazer(fita_1, fitb_1, fitc_1, fitcp_1, header=FALSE, type = 'latex')
```